It is Byteman's birthday today. There are $n$ children at his birthday party (including Byteman). The children
are numbered from $1$ to $n$. Byteman's parents have prepared a big round table and they have placed $n$ chairs
around the table. When the children arrive, they take seats. The child number 1 takes one of the seats. Then
the child number 2 takes the seat on the left. Then the child number 3 takes the next seat on the left, and so
on. Finally the child number $n$ takes the last free seat, between the children number 1 and $n - 1$.

Byteman's parents know the children very well and they know that some of the children will be noisy, if
they sit too close to each other. Therefore the parents are going to reseat the children in a specific order. Such
an order can be described by a permutation $p_1, p_2, \ldots , p_n$ ($p_1, p_2, \ldots, p_n$ are distinct integers from 1 to n)~---
child $p_1$ should sit between $p_n$ and $p_2$, child $p_i$ (for $i = 2,3, \ldots , n-1)$ should sit between $p_{i - 1}$ and $p_{i + 1}$, and
child $p_n$ should sit between $p_{n - 1}$ and $p_1$. Please note, that child $p_1$ can sit on the left or on the right from child $p_n$.

To seat all the children in the given order, the parents must move each child around the table to the left or
to the right some number of seats. For each child, they must decide how the child will move~--- that is, they
must choose a direction of movement (left or right) and distance (number of seats). On the given signal, all
the children stand up at once, move to the proper places and sit down.

The reseating procedure throws the birthday party into a mess. The mess is equal to the largest distance
any child moves. The children can be reseated in many ways. The parents choose one with minimum mess.
Help them to find such a way to reseat the children.

Your task is to write a program that:

\begin{itemize}
\item reads from the standard input the number of the children and the permutation describing the desired
order of the children,

\item determines the minimum possible mess,

\item writes the result to the standard output
\end{itemize}