You are going to hold an international programming contest in a rectangular hall, which has $ H \cdot W $ seats arranged in $ H $ rows and $ W $ columns. The rows are numbered from $ 0 $ through $ H-1 $ and the columns are numbered from $ 0 $ through $ W-1. $ The seat in row $ r $ and column $ c $ is denoted by $ (r, c) $ . You invited $ H \cdot W $ contestants, numbered from 0 through $ H \cdot W - 1. $ You also made a seating chart, which assigns the contestant $i$ $( 0 \le i \le H \cdot W-1 )$ to the seat $ (R_i, C_i).$ The chart assigns exactly one contestant to each seat. 

A set of seats in the hall $ S $ is said to be \bf{rectangular} if there are integers $ r_1 $ , $ r_2 $ , $ c_1 $ , and $ c_2 $ satisfying the following conditions:

\begin{itemize}
\item $ 0 \le r_1 \le r_2 \le H-1 $ 
\item $ 0 \le c_1 \le c_2 \le W-1 $ 
\item $ S $ is exactly the set of all seats $ (r, c) $ such that $ r_1 \le r \le r_2 $ and $c_1 \le c \le c_2$. 
\end{itemize}

A rectangular set consisting of $ k $ seats $ ( 1 \le k \le H \cdot W) $ , is \bf{beautiful} if the contestants whose assigned seats are in the set have numbers from $ 0 $ through $ k-1 $ . The \bf{beauty} of a seating chart is the number of beautiful rectangular sets of seats in the chart. 

After preparing your seating chart, you receive several requests to swap two seats assigned to two contestants. More precisely, there are $ Q $ such requests numbered from $ 0 $ through $ Q-1 $ in chronological order. The request $ j$ $(0 \le j \le Q-1) $ is to swap the seats assigned to contestants $ A_j $ and $ B_j $ . You accept each request immediately and update the chart. After each update, your goal is to compute the beauty of the current seating chart. 

\bf{Implementation details}

You should implement the following procedure and function:

\t{give_initial_chart(int H, int W, int[] R, int[] C)}

\begin{itemize}
\item $ H, W $ : the number of rows and the number of columns.
\item $ R, C $ : arrays of length $ H \cdot W $ representing the initial seating chart.
\item This procedure is called exactly once, and before any call to \t{swap_seats}.
\end{itemize}

\t{int swap_seats(int a, int b) }

\begin{itemize}
\item This function describes a request to swap two seats. 
\item $ a, b: $ contestants whose seats are to be swapped.
\item This function is called $ Q $ times.
\item This function should return the beauty of the seating chart after the swap 
\end{itemize}

\bf{Constraints}

\begin{itemize}
\item $ 1 \le H $ 
\item $ 1 \le W $ 
\item $ H \cdot W \le 1\,000\,000 $ 
\item $ 0 \le Ri \le H-1 $ for all $ i: 0 \le i \le H \cdot W-1 $ 
\item $ 0 \le Ci \le W-1 $ for all $ i: 0 \le i \le H \cdot W-1 $ 
\item $ (R_i, C_i) \neq (R_j, C_j) $ for all $ i, j: 0 \le i < j \le H \cdot W-1 $ 
\item $ 1 \le Q \le 50\,000 $ 
\item $ 0 \le a \le H \cdot W -1 $ for any call to \t{swap_seats}
\item $ 0 \le b \le H \cdot W -1 $ for any call to \t{swap_seats}
\item $ a \neq b $ for any call to \t{swap_seats}
\end{itemize} 

\bf{Sample grader}

The sample grader reads the input in the following format:

\begin{tabular}{ccccc}\\
line& $ 1 $ &:& $ H$ $W$ $Q$ &\\
line& $ 2+i $ &:& $R_i$ $C_i$ & $ (0 \le i \le H \cdot W-1) $ \\
line& $ 2+H \cdot W+j $ &:& $A_j$ $B_j$ & $ (0 \le j \le Q-1) $ \\
\end{tabular}

Here, $ A_j $ and $ B_j $ are parameters for the call to \t{swap_seats} for the request $j.$ 

The sample grader prints your answers in the following format:

\begin{tabular}{ccccc}
line& $ 1+j $ &:&the return value of \t{swap_seats} for the request $ j $ & $ (0 \le j \le Q-1) $ 
\end{tabular}
