This is an output-only problem. That means, that you don't need to submit your solution, but only need to submit outputs for given set of inputs. You can download test data in a problem materials section. It is an archive containing input files 01, 02, 03, \dots. You need to submit a single zip-archive containing your outputs 01.out, 02.out, 03.out, \dots in the root of the archive.  An archive can contain no answers for some of tests, you'll receive ``\t{Wrong Answer}'' verdict in these tests.

Consider a Two-Operation Machine (TOM for short) with nine registers, numbered $1 \ldots 9$. 

Each register stores a non-negative integer in the range $0 \ldots 1000$. The machine has two operations:

S $i$ $j$ --- Store one plus the value of register $i$ into register $j$. Note that $i$ may equal $j$.

P $i$ Print the value of register $i$.

A TOM program includes a set of initial values for the registers and a sequence of operations. Given an integer $N$ ($0 \le N \le 255$), generate a TOM program that prints the decreasing sequence of integers $N, N-1, N-2, \ldots, 0$. The maximum number of consecutive S-operations should be as small as possible.

Example of a TOM program and its execution for N=2:

\begin{tabular}{|c|c|c|}
\hline
Operation & New  Register Values & Printed Value \\ 
& 1 2 3 4 5 6 7 8 9 &  \\ \hline
Initial values & 0 2 0 0 0 0 0 0 0 & \\ \hline
P 2 & 0 2 0 0 0 0 0 0 0 & 2 \\ \hline
S 1 3 & 0 2 1 0 0 0 0 0 0 & \\ \hline
P 3 & 0 2 1 0 0 0 0 0 0 & 1 \\ \hline
P 1 & 0 2 1 0 0 0 0 0 0 & 0 \\ \hline
\end{tabular}

Input cases are numbered 1 through 16 and are available via the contest server.