You are visiting a park which has $N$ islands. From each island $i$, exactly one bridge was constructed. The length of that bridge is denoted by $L_i$. The total number of bridges in the park is $N$. Although each bridge was built from one island to another, now every bridge can be traversed in both directions. Also, for each pair of islands, there is a unique ferry that travels back and forth between them. 

Since you like walking better than riding ferries, you want to maximize the sum of the lengths of the bridges you cross, subject to the constraints below.
\begin{itemize}
\item You can start your visit at an island of your choice.
\item You may not visit any island more than once.
\item At any time you may move from your current island $S$ to another island $D$ that you have not visited before. You can go from $S$ to $D$ either by:
\begin{itemize}
\item Walking: Only possible if there is a bridge between the two islands. With this option the length of the bridge is added to the total distance you have walked, or
\item Ferry: You can choose this option only if $D$ is not reachable from $S$ using any combination of bridges and/or previously used ferries. (When checking whether it is reachable or not, you consider all paths, including paths passing through islands that you have already visited.)
\end{itemize}
\end{itemize}

Note that you do not have to visit all the islands, and it may be impossible to cross all the bridges.

Write a program that, given the $N$ bridges along with their lengths, computes the maximum distance you can walk over the bridges obeying the rules described above.