The sample grader first calls \texttt{construct\_instructions(s, n, k, q)}.  If this call violates some
constraint described in the problem statement, the sample grader prints one of the error messages listed at the end of this section and exits. Otherwise, the sample grader first
prints each instruction appended by \texttt{construct\_instructions(s, n, k, q)}, in order. For $store$
instructions, $v$ is printed from index $0$ to index $b-1$.

Then, the sample grader processes test cases in order. For each test case, it runs the constructed
program on the input of the test case.

For each $print(t)$ operation, let $d[0], d[1], \ldots, d[n-1]$ be a sequence of integers, such that for each $i$ ($0 \leq i \leq n-1$) $d[i]$  is the integer value of the sequence of bits $i\cdot k$ to $(i + 1)\cdot k-1$ of
register $t$ (when the operation is executed). The grader prints this sequence in the following format: \texttt{register} $t$: $d[0]\ d[1]\ldots \ d[n-1]$.

Once all instructions have been executed, the sample grader prints the output of the program.

If $s = 0$, the output of the sample grader for each test case is in the following format:
\begin{itemize}
\item $c[0]$.
\end{itemize}

If $s = 1$, the output of the sample grader for each test case is in the following format:
\begin{itemize}
\item $c[0]\ c[1]\ldots \ c[n-1]$.
\end{itemize}

After executing all test cases, the grader prints \texttt{number of instructions}: $X$, where $X$ is the number of instructions in your program.


The grading of your solution may result in one of the following error messages:

\begin{itemize}
\item \texttt{Invalid index}: an incorrect (possibly negative) register index was provided as parameter $t$,
$x$ or $y$ for some call of one of the procedures.
\item \texttt{Value to store is not b bits long}: the length of $v$ given to  \texttt{append\_store}, is not equal to $b$.
\item \texttt{Invalid shift value}: the value of $p$ given to \texttt{append\_left} or \texttt{append\_right}, is not between $0$ and $b$ inclusive.
\item \texttt{Too many instructions}: your procedure attempted to append more than $q$ instructions.
\end{itemize}
