It was told by Scheherazade that far away, in the middle of the desert, there is a lake. Originally this lake had $F$ fish in it. $K$ different kinds of gemstones were chosen among the most valuable on Earth, and to each of the $F$ fish exactly one gem was given for it to swallow. Note, that since $K$ might be less than $F$, two or more fish might swallow gems of the same kind.

As time went by, some fish ate some of the other fish. One fish can eat another if and only if it is at least twice as long (fish $A$ can eat fish $B$ if and only if $L_A \ge 2 \cdot L_B$). There is no rule as to when a fish decides to eat. One fish might decide to eat several smaller fish one after another, while some fish may decide not
to eat any fish, even if they can.  When a fish eats a smaller one, its length doesn't change, but the gems in the stomach of the smaller fish end up undamaged in the stomach of the larger fish.

Scheherazade has said that if you are able to find the lake, you will be allowed to take out one fish and keep all the gems in its stomach for yourself. You are willing to try your luck, but before you head out on the long journey, you want to know how many different combinations of gems you could obtain by catching a single fish.

Write a program that given the length of each fish and the kind of gemstone originally swallowed by each fish, finds the number of different combinations of gems that can end up in the stomach of any fish, modulo some given integer $M$. A combination is defined only by the number of gems from each of the $K$ kinds. There is no notion of order between gems, and any two gems of the same kind are indistinguishable.