You are the proud owner of two robots that are located in separate rectangular mazes. Square (1, 1) in a maze is the square in the upper-left corner, which is the north-west corner. Maze $i$ (i = 1, 2) has a set of $G_i$ ($0 \leq G_i \leq 10$) guards trying to capture the robots by patrolling back and forth on a straight patrol path. Your goal is to determine a sequence of commands such that the robots exit the mazes without either robot being captured by a guard.

At the beginning of each minute, you broadcast the same command to both robots. Each command is a direction (north, south, east, or west). A robot moves one square in the direction of the command, unless the robot would collide with a wall, in which case the robot does not move for that minute. A robot exits the maze by walking out of it. A robot ignores commands after it has exited its maze.

Guards move one square at the beginning of each minute, at the same time as the robots. Each guard begins at a given square facing a given direction and moves forward one square per minute until the guard has moved one fewer square than the number of squares in his patrol path. The guard then turns around instantaneously and walks in the opposite direction back to his starting square, where he turns around again and repeats his patrol path until each robot has exited its maze.

A guard's patrol will not require the guard to walk through walls or exit the maze. Although guard patrols may overlap, no two guards will ever collide: they will never occupy the same square at the end of a minute, and they will not exchange squares with each other during a minute. A guard in a maze will not start in the same square as the
robot in that maze.

A guard captures a robot if the guard occupies the same square at the end of a minute as the robot, or if the guard and the robot exchange squares with each other during a minute. Given two mazes (each no larger than $20\times 20$) along with the initial square of each robot and the patrol paths of the guards in each maze, determine a sequence of commands for which the robots exit without being caught by the guards. Minimize the time it takes for the later robot to exit its maze. If the robots exit at different times, the time at which the earlier robot exited does not matter.