A game called Memory is played using $50$ cards. Each card has one of the letters from A to Y (ASCII $65$ to $89$) printed on the face, so that each letter appears on
exactly two cards. The cards are shuffled into some random order and dealt face down on the table.

Jack plays the game by turning two cards face up so the letters are visible. For each of
the $25$ letters Jack gets a candy from his mother the first time he sees both copies of
the letter on the two face up cards. For example, the first time Jack turns over both
cards that contain the letter M, he gets a candy. Regardless of whether the letters were
equal or not, Jack then turns both cards face down again. The process is repeated until
Jack receives $25$ candies --- one for each letter.

You are to implement a procedure play that plays the game. Your implementation
should call the procedure \t{faceup(C)} which is implemented by the grader. $C$ is a
number between $1$ and $50$ denoting a particular card you wish to be turned face up.
The card $C$ must not currently be face up. \t{faceup(C)} returns the character that is printed on the card $C$.

After every second call to \t{faceup}, the grader automatically turns both cards face down
again.

Your procedure play may only terminate once Jack has received all $25$ candies. It is
allowed to make calls to \t{faceup(C)} even after the moment when Jack gets the last
candy.

The following is one possible sequence of calls your procedure play could make, with
explanations.

\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|}
\hline
Call & Returned value & Explanation \\ 
\hline
faceup(1) & `B' & Card $1$ contains B. \\ 
\hline 
faceup(7) & `X' & \parbox{13cm}{\centering \vspace{2mm}Card $7$ contains X. The letters are not equal. The grader automatically turns cards $1$ and $7$ face down.\\\vspace{2mm}} \\ \hline
faceup(7) & `X' & Card $7$ contains X.\\ 
\hline
faceup(15) & `O' &\parbox{13cm}{\centering \vspace{2mm} Card $15$ contains O. The letters are not equal. The grader automatically turns cards $7$ and $15$ face down.\\\vspace{2mm}} \\ 
\hline
faceup(50) & `X' & Card $50$ contains X.\\ 
\hline
faceup(7) & `X' & \parbox{13cm}{\centering \vspace{2mm}Card $7$ contains X. Jack gets his first candy. The grader automatically turns cards $50$ and $7$ face down.\\\vspace{2mm}}\\ \hline
faceup(7) & `X' & Card $7$ contains X. \\ 
\hline
faceup(50) & `X' & \parbox{13cm}{\centering \vspace{2mm}Card $50$ contains X. Equal letters, but Jack gets no candy. The grader automatically turns cards $7$ and $50$ face down. \\\vspace{2mm}}\\ 
\hline
faceup(2) & `B' & Card $2$ contains B. \\ 
\hline
... & ... & Some function calls were omitted \\ \hline
faceup(1) & `B' & Card $1$ contains B. \\ \hline 
faceup(2) & `B' & Card $2$ contains B. Jack gets his 25th candy. \\ \hline 
\end{tabular}
\end{center}