Jian-Jia is a young boy who loves playing games. When he is asked a question, he prefers playing games rather than answering directly. Jian-Jia met his friend Mei-Yu and told her about the flight network in Taiwan. There are $n$ cities in Taiwan (numbered $0, \ldots, n - 1$), some of which are connected by flights. Each flight connects two cities and can be taken in both directions.

Mei-Yu asked Jian-Jia whether it is possible to go between any two cities by plane (either directly or indirectly). Jian-Jia did not want to reveal the answer, but instead suggested to play a game. Mei-Yu can ask him questions of the form ``Are cities $x$ and $y$ \texttt{directly} connected with a flight?'', and Jian-Jia will answer such questions immediately. Mei-Yu will ask about every pair of cities exactly once, giving $r = \frac{n(n - 1)}{2}$ questions in total. Mei-Yu wins the game if, after obtaining the answers to the first $i$ questions for some $i < r$, she can infer whether or not it is possible to travel between every pair of cities by flights (either directly or indirectly). Otherwise, that is, if she needs all $r$ questions, then the winner is Jian-Jia.

In order for the game to be more fun for Jian-Jia, the friends agreed that he may forget about the real Taiwanese flight network, and invent the network as the game progresses, choosing his answers based on Mei-Yu's previous questions. Your task is to help Jian-Jia win the game, by deciding how he should answer the questions

\textbf{Task}

Please write a program that helps Jian-Jia win the game. Note that neither Mei-Yu nor Jian-Jia knows the strategy of each other. Mei-Yu can ask about pairs of cities in any order, and Jian-Jia must answer them immediately without knowing the future questions. You need to implement the following two functions.

\begin{itemize}
\item \texttt{void initialize(int n)}~--- We will call your \texttt{initialize} first. The parameter $n$ is the number of cities.
\item \texttt{int hasEdge(int u, int v)}~--- Then we will call \texttt{hasEdge} for $r = \frac{n(n - 1)}{2}$ times. These calls represent Mei-Yu's questions, in the order that she asks them. You must answer whether there is a direct flight between cities $u$ and $v$. Specifically, the return value should be $1$ if there is a direct flight, or $0$ otherwise.
\end{itemize}