There are $N$ radio towers in Jakarta.
The towers are located along a straight line and numbered from $0$ to $N - 1$ from left to right.
For each $i$ such that $0 \le i \le N - 1$, the height of tower $i$ is $H[i]$ metres.
The heights of the towers are \textbf{distinct}.

\newcommand{\gt}{\textgreater} 
\newcommand{\lt}{\textless} 

For some positive interference value $\delta$, a pair of towers $i$ and $j$ (where $0 \le i \lt j \le N - 1$) can communicate with each other if and only if there is an intermediary tower $k$, such that
\begin{itemize}
    \item tower $i$ is to the left of tower $k$ and tower $j$ is to the right of tower $k$, that is, $i \lt k \lt j$, and
    \item the heights of tower $i$ and tower $j$ are both at most $H[k] - \delta$ metres.

\end{itemize}

Pak Dengklek wants to lease some radio towers for his new radio network.
Your task is to answer $Q$ questions of Pak Dengklek which are of the following form:
given parameters $L\ R$ and $D$ ($0 \le L \le R \le N - 1$ and $D > 0$), what is the maximum number of towers Pak Dengklek can lease, assuming that

\begin{itemize}
 \item Pak Dengklek can only lease towers with indices between $L$ and $R$ (inclusive), and
 \item the interference value $\delta$ is $D$, and
 \item any pair of radio towers that Pak Dengklek leases must be able to communicate with each other. 

\end{itemize}
Note that two leased towers may communicate using an intermediary tower $k$, regardless of whether tower $k$ is leased or not.


\textbf{Implementation Details}

You should implement the following procedures:

\begin{itemize}
    \item \texttt{void init(int N, int[] H)}
\begin{itemize}

\item $N$: the number of radio towers.
\item $H$: an array of length $N$ describing the tower heights.
\item This procedure is called exactly once, before any calls to \texttt{max\_towers}.
\end{itemize}

\item \texttt{int max\_towers(int L, int R, int D)}
\begin{itemize}

\item $L$, $R$: the boundaries of a range of towers.
\item $D$: the value of $\delta$.
\item This procedure should return the maximum number of radio towers Pak Dengklek can lease for his new radio network if he is only allowed to lease towers between tower $L$ and tower $R$ (inclusive) and the value of $\delta$ is $D$.
\item This procedure is called exactly $Q$ times.
\end{itemize}

\end{itemize}


