This story takes place a long time ago, when the world was new and the IOI had not yet
been dreamt.

Serpent lives in a land which has $N$ billabongs (water holes), numbered $0, \dots, N ­- 1$.
There are $M$ bidirectional trails, joining pairs of billabongs, which Serpent can travel
along. Each pair of billabongs is connected (directly or indirectly) by at most one sequence
of trails, though some pairs of billabongs may not be connected at all (thus, $M \leq N - ­1$ ). Each
trail takes a certain number of days for Serpent to travel along it: this number may be
different for each trail.

Serpent's friend, Kangaroo, wishes to make $N -­ M ­- 1$ new trails, so that it is possible for
Serpent to travel between any pair of billabongs. Kangaroo can create trails between any
pair of billabongs, and every trail that Kangaroo creates will take $L$ days for Serpent to
travel along it.

Additionally, Kangaroo wants to make Serpent's travels as fast as possible. Kangaroo will
build the new trails so that the longest travel time between any two billabongs is as small as
possible. Help Kangaroo and Serpent determine the longest travel time between any two
billabongs, after Kangaroo has built the new trails in this way.

You should submit a file implementing the function $travelTime()$, as follows:

\t{int travelTime(int N, int M, int L, int A[], int B[], int T[]);}

This function should calculate the greatest travel time (measured in days) between any pair
of billabongs, assuming that Kangaroo has added $N ­- M ­- 1$ trails in such a way that all
billabongs are connected and this greatest travel time is as small as possible.

Parameters:
\begin{itemize}
\item $N$: The number of billabongs.
\item $M$: The number of trails that already exist.
\item $L$: The time in days that it takes Serpent to travel along a new trail.
\item $A$, $B$ and $T$: Arrays of length $M$ that specify the endpoints and travel time of
each pre­existing trail, so that the $i^{th}$ trail joins billabongs $A[i­-1]$ and $B[i - 1]$,
and takes $T[i-­1]$ days to travel in either direction.
\item \textit{Returns:} The greatest travel time between any pair of billabongs, as described above.
\end{itemize}