This is an output-only problem. That means, that you don't need to submit your solution, but only need to submit outputs for given set of inputs. You can download test data in a problem materials section. It is an archive containing input files 01, 02, 03, \dots. You need to submit a single zip-archive containing your outputs 01.out, 02.out, 03.out, \dots in the root of the archive.  An archive can contain no answers for some of tests, you'll receive ``\t{Wrong Answer}'' verdict in these tests.

Azerbaijan is famous for its carpets.
As a master carpet designer you want to make a new design by drawing a \texttt{broken line}.
A broken line is a sequence of $t$ line segments in a two-dimensional plane, which is defined by a sequence of $t+1$ points $p_0, \ldots, p_t$ as follows.
For each $0 \leq j \leq t-1$ there is a segment connecting points $p_j$ and $p_{j+1}$.

In order to make the new design, you have already marked $n$ \texttt{dots} in a two-dimensional plane.
The coordinates of dot $i$ ($1 \leq i \leq n$) are $(x[i], y[i])$.
\texttt{No two dots have the same $x$ or the same $y$ coordinate.}

You now want to find a sequence of points $(sx[0], sy[0]), (sx[1], sy[1]), \ldots, (sx[k], sy[k])$, which defines a broken line that
\begin{itemize}
\item starts at $(0,0)$ (that is, $sx[0]=0$ and $sy[0]=0$),
\item contains all of the dots (not necessarily as the endpoints of the segments), and
\item consists solely of horizontal or vertical segments (two consecutive points defining the broken line have an equal x or y coordinate).
\end{itemize}

The broken line is allowed to intersect or overlap itself in any way. Formally, each point of the plane may belong to any number of segments of the broken line.

This is an output-only task with partial scoring.
You are given $10$ input files specifying the locations of dots.
For each input file, you should submit an output file describing a broken line with the required properties.
For each output file that describes a valid broken line your score depends on the \texttt{number of segments} in the broken line (see Scoring below).

You are not supposed to submit any source code for this task.

